\plaintitle

### 2017-01-08 drafts/labor/discussion.tex
revisions of the discussion and conclusion

\begin{document}
\section{Discussion}
\topic{In our analysis of on--demand work via the piecework lens, three issues arose:}
\begin{inlinelist}
  \item \namerefl{sec:perilousProblemsPredicting},
  \item \namerefl{sec:polarizationOfCrowdWork}, and
  \item \namerefl{sec:whatShouldBeTheFuture}.
\end{inlinelist}
We will attempt to grapple with these questions here explicitly.

\subsection{The Hazards of Predicting the Future}\label{sec:perilousProblemsPredicting}
The past can't be a perfect predictor for the future;
as \citeauthor{scholz2012digital} points out,
``it would be wrong to conclude that
in the realm of digital labor
there is nothing new under the sun''
\cite{scholz2012digital}.
Our analysis is limited by the differences, foreseen and unforeseen, between historical piecework and modern on--demand work.
For example, many of the challenges that \DO~overcame in crowd collective action, such as designing for trustworthiness and ensuring anonymity, were relatively unique challenges precipitated by the affordances of the internet.
For example, unlike physical work environments, people can (and often do) contribute to online communities in a one--off manner
\cite{mcinnis2016one}.
The internet makes this kind of loose affiliation feasible.
While we have attempted to understand the likely overlaps and differences between history and modern day, no analysis is perfect.
% articulated in the discussion about
% organizing people and the challenges therein
% \cite{dynamo}, as well as for
% many of the rhizomatic features \citeauthor{miller2011understanding}
% discusses
% \cite{miller2011understanding}).

@@

In particular, the predictions that have emerged surrounding crowd work have run the spectrum
from deep pessimism~\cite{fort2011amazon} to exuberant optimism~\cite{crowdworkFuture}.
In the next section, we will use
the piecework foundation which informed our case studies
to trace out possible dystopian and utopian futures for on--demand labor.

@@

\subsection{A Research Agenda}\label{sec:whatShouldBeTheFuture}
Piecework also helps bring into focus the
areas of research that might bear the most fruit.
We return to the three questions that motivated this paper:
\begin{inlinelist}
  \item ``\namerefl{sec:complexity}?''
  \item ``\namerefl{sec:decomposition}?''
        and
  \item ``\namerefl{sec:relationships}?''
\end{inlinelist}.

>>>>

\begin{document}
\section{Discussion}
\topic{In our analysis of on--demand work via the piecework lens, three issues arise:}
\begin{inlinelist}
  \item \namerefl{sec:perilousProblemsPredicting},
  \item \namerefl{sec:polarizationOfCrowdWork}, and
  \item \namerefl{sec:whatShouldBeTheFuture}.
\end{inlinelist}
We will attempt to grapple with these questions here explicitly.

\subsection{The Hazards of Predicting the Future}\label{sec:perilousProblemsPredicting}
The past can't be a perfect predictor for the future;
as \citeauthor{scholz2012digital} points out,
``it would be wrong to conclude that
in the realm of digital labor
there is nothing new under the sun''
\cite{scholz2012digital}.
Our analysis is limited by the differences, foreseen and unforeseen, between historical piecework and modern on--demand work.
%For example, many of the challenges that \DO~overcame in crowd collective action, such as designing for trustworthiness and ensuring anonymity, were relatively unique challenges precipitated by the affordances of the internet.
For example, unlike physical work environments, people can (and often do) contribute to online communities in a one--off manner
\cite{mcinnis2016one}.
The internet makes this kind of loose affiliation feasible.
While we have attempted to understand the likely overlaps and differences between history and modern day, no analysis is perfect.
% articulated in the discussion about
% organizing people and the challenges therein
% \cite{dynamo}, as well as for
% many of the rhizomatic features \citeauthor{miller2011understanding}
% discusses
% \cite{miller2011understanding}).

@@

%In particular, the predictions that have emerged in the literature surrounding the future of crowd work have run the spectrum
%from deep pessimism~\cite{fort2011amazon} to exuberant optimism~\cite{crowdworkFuture}.
%In the next section, we will use
%the piecework foundation which informed our case studies
%to trace out possible dystopian and utopian futures for on--demand labor.

\msb{Shouldn't we bring up the discussion from the rebuttal about history/future connections here?}

@@

\subsection{A Research Agenda}\label{sec:whatShouldBeTheFuture}
Piecework also helps bring into focus the
areas of research that might bear the most fruit.
We return to the three questions that motivated this paper:
\begin{inlinelist}
  \item \nameref{sec:complexity}?
  \item \nameref{sec:decomposition}?
  \item \nameref{sec:relationships}?
\end{inlinelist}
